
\cvsection[]{Personal Projects}

\cvevent{Shopping Queue}{}{July 2020}{Ottawa, ON}
\github{\href{https://github.com/larryworm1127/Shopping-Queue}{larryworm1127/Shopping-Queue}}

\vspace{5pt}

\begin{itemize}
	\item Created a web app that helps control the flow of shoppers in response to social distancing policies for COVID-19.
	\item Built using React.js for frontend, with an Express REST APIs server and MongoDB for data storage.
\end{itemize}

\divider

\cvevent{XiangQi.js}{}{August 2020}{Ottawa, ON}
\github{\href{https://github.com/larryworm1127/XiangQi.js}{larryworm1127/XiangQi.js}}

\vspace{5pt}

\begin{itemize}
	\item Created a JavaScript library that embeds XiangQi board game onto the web using JavaScript DOM manipulation.
\end{itemize}

\divider

\cvevent{Android Game}{}{December 2019}{Toronto, ON}
\github{\href{https://github.com/larryworm1127/AdventureOfPost}{larryworm1127/AdventureOfPost}}

\vspace{5pt}

\begin{itemize}
	\item Created a three-part Android game using Java, Gradle and SQLite.
    \item Implemented user authentication, game statistics tracking using SQLite database.
    \item Employed SOLID principles, MVP architecture and other object-oriented design patterns.
	\item Designed the project, oral presentation, UML diagrams in collaboration with five other peers.
\end{itemize}

\divider

\cvevent{NBA Daily}{}{Apirl 2019}{Ottawa, ON}
\github{\href{https://github.com/larryworm1127/nba\_daily}{larryworm1127/nba\_daily}}

\vspace{5pt}

\begin{itemize}
	\item Built a web app that displays the NBA stats in a more accessible way using Django.
    \item Used SQLite to store and access all scrapped NBA stats.
\end{itemize}

\divider

\cvevent{Autocomplete Engine}{}{December 2018}{Toronto, ON}
\github{\href{https://github.com/larryworm1127/autocomplete}{larryworm1127/autocomplete}}

\vspace{5pt}

\begin{itemize}
	\item Created an autocomplete engine that generates autocomplete results from given data.
	\item Implemented the autocomplete algorithm using weighted tree data structures.
\end{itemize}

\divider

\cvevent{PyBoardGame}{}{September 2018}{Ottawa, ON}
\github{\href{https://github.com/larryworm1127/PyBoardGame}{larryworm1127/PyBoardGame}}

\vspace{5pt}

\begin{itemize}
	\item Built a simple board games web app using Flask and JQuery.
	\item Implemented a computer Tic Tac Toe player using minimax algorithm.
\end{itemize}
