%%%%%%%%%%%%%%%%%
% This is an example CV created using altacv.cls (v1.1.4, 27 July 2018) written by
% LianTze Lim (liantze@gmail.com), based on the
% Cv created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you want to use \orcid or the
%% academicons icons, add "academicons"
%% to the \documentclass options.
%% Then compile with XeLaTeX or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper]{altacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages.
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols.
%% When using the "academicons" option,
%% Compile with LuaLaTeX for best results. If you
%% want to use XeLaTeX, you may need to install
%% Academicons.ttf in your operating system's font %% folder.


% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1cm,bottom=1cm}

% Change the font if you want to.

% If using pdflatex:
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage{hyperref}
\usepackage{fontawesome}

% If using xelatex or lualatex:
% \setmainfont{Lato}

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{black}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\begin{document}
\name{Le Rong (Larry) Shi}
\tagline{Software Developer}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{\href{mailto:shilerong@gmail.com}{shilerong@gmail.com}}
  \phone{343-777-8457}
  \homepage{\href{https://larryworm1127.github.io/}{larryworm1127.github.io}}
  \linkedin{\href{https://www.linkedin.com/in/larry-shi-11479914b/}{linkedin.com/in/larry-shi-11479914b/}}
  \github{\href{https://github.com/larryworm1127}{github.com/larryworm1127}}
}

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Include the sidebar
\marginpar{\vspace*{-85pt}\raggedright\input{page1sidebar}}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvsection[]{Experience}

\cvevent{Software Developer in Test - Intern}{Merchant Link}{May 2019 -- August 2019}{Ottawa, ON}
\begin{itemize}
\item Used Python to create scripts that simulates behaviors of a pinpad to help automate testing of company product.
\item Performed stress testing on company product to evaluate its ability to process transactions.
\item Used Python to create an experimental tool that captures product network activities and diagnose for pinpad issues.
\end{itemize}


\cvsection[]{Personal Projects}

\cvevent{\href{https://github.com/larryworm1127/PyBoardGame}{PyBoardGame}}{}{July 2018 -- September 2018}{Ottawa, ON}
\begin{itemize}
    \item A web project written in Python (Flask) that allows users to play simple board games on the website. Including Tic Tac Toe and Sudoku.
    \item A computer player is implemented using minimax algorithm in Python while the rest of game logic is implemented in JavaScript.
    \item The website also contains well documented game strategies pages.
\end{itemize}

\divider

\cvevent{\href{https://github.com/larryworm1127/nba\_daily}{NBA Daily}}{}{Apirl 2019 -- Ongoing}{Ottawa, ON}
\begin{itemize}
    \item A web project written in Python (Django) that scraps NBA stats from NBA website using API and displays the data in a more accessible way.
    \item Used SQLite alongside Django model to store and access all scapped data.
    \item Currently trying to integrate React with Django Rest Framework to create better looking and functinal web pages.
\end{itemize}

\divider

\cvevent{\href{https://github.com/larryworm1127/RecipeGenerator}{Recipe Generator}}{}{May 2018 -- September 2018}{Ottawa, ON}
\begin{itemize}
	\item A GUI app written in Python (Tkinter) that helps with generating custom Minecraft recipe in the form of JSON file for Minecraft modding.
	\item The app validates user inputs to make sure the generated recipe file can be used without any error.
\end{itemize}


\cvsection[]{Extracurricular Activities}

\cvevent{Volunteer}{Stillwater Creek Retirement Home}{July 2014 -- June 2018}{Ottawa, ON}
\begin{itemize}
    \item Perform music with a group named "Music in Motion" in the retirement home.
    \item Organized "Music in Motion" performances.
    \item Help kitchen serve out ice creams to seniors in the retirement home.
\end{itemize}


\cvsection{Languages}

\cvskill{English}{5}
\cvskill{Mandarin}{4}

\end{document}
